The \kepler Smear Campaign I: An Asteroseismic Catalogue of Bright Red Giants

### 2018-07-30 paper/ms.tex
untrack
space
include hr diagram and gaia distances

@@

\subsection{Red Giants}
\label{rgs}
\subsection{Chemical Composition}
place [X/Fe] vs [Fe/H] diagrams here and discuss which Galactic populations these stars come from. May also want to discuss how these span the typical Galactic populations and can act as benchmark stars for APOGEE or other large surveys 
\subsection{Other Stars}
\label{other}

@@

>>>>

\begin{figure*}
\noindent\includegraphics[width=15cm,keepaspectratio]{gaia_kepler_hr.png}

\caption{\label{hrdiagram}
Hertzsprung-Russell diagram of the Smear Campaign stars (orange and teal) situated in the entire \kepler sample (black), using the Bedell \texttt{gaia-kepler.fun} crossmatch and calibrated distances from \citet{gaiadists}. The smear sample includes giants and hot main-sequence stars. Those giants for which TRES spectroscopy have been obtained are highlighted in teal.}
\end{figure*}

@@

\subsection{Red Giants}
\label{rgs}

\subsection{Chemical Composition}
place [X/Fe] vs [Fe/H] diagrams here and discuss which Galactic populations these stars come from. May also want to discuss how these span the typical Galactic populations and can act as benchmark stars for APOGEE or other large surveys

\subsection{Other Stars}
\label{other}

@@

This work has made use of data from the European Space Agency (ESA) mission
{\it Gaia} (\url{https://www.cosmos.esa.int/gaia}), processed by the {\it Gaia}
Data Processing and Analysis Consortium (DPAC,
\url{https://www.cosmos.esa.int/web/gaia/dpac/consortium}). Funding for the DPAC
has been provided by national institutions, in particular the institutions
participating in the {\it Gaia} Multilateral Agreement. This work made use of the gaia-kepler.fun crossmatch database created by Megan Bedell.
